\section{Introduction}

Modern AI systems require robust infrastructure for secure hardware attestation, model verification, and resource management. \sysname{} addresses these challenges through a comprehensive microservices architecture built with Rust, emphasizing performance, security, and reliability. Additionally, we demonstrate how small language models can achieve advanced reasoning capabilities through structured deep thinking approaches.

\subsection{System Overview}

\sysname{} consists of five core microservices:
\begin{itemize}
    \item \textbf{API Gateway}: The entry point for external clients, handling request routing, rate limiting, and initial authentication.
    \item \textbf{Authentication Service}: Manages user accounts, authentication, and JWT token issuance.
    \item \textbf{Hardware Attestation Service}: Performs hardware checks, AI model verification, and compliance validation.
    \item \textbf{Document Service}: Handles file uploads, metadata storage, and S3 integration.
    \item \textbf{Resource Management Service}: Allocates compute resources, manages quotas, and monitors usage.
\end{itemize}

\subsection{Key Features}

\begin{itemize}
    \item \textbf{Security}: JWT-based authentication, bcrypt password hashing, and secure secret management (Vault).
    \item \textbf{Scalability}: Docker and Kubernetes-based deployment with horizontal scaling.
    \item \textbf{Observability}: Comprehensive monitoring (Prometheus, Grafana, distributed tracing).
    \item \textbf{Performance}: High-performance async web services (Actix-web + Tokio).
    \item \textbf{Reliability}: Robust error handling, graceful degradation, automated recovery.
    \item \textbf{Deep Thinking}: Monte Carlo Tree Search with process preference modeling for advanced reasoning.
\end{itemize}

\subsection{Document Structure}

This document is organized as follows:
\begin{itemize}
    \item \textbf{Section 2}: Deep thinking methodology for math reasoning
    \item \textbf{Section 3}: System architecture and implementation
    \item \textbf{Section 4}: Deployment, monitoring, and maintenance
    \item \textbf{Section 5}: Conclusion and future directions
    \item \textbf{Appendix}: Additional experiments and implementation details
\end{itemize}

The documentation aims to serve as a comprehensive guide for both AI agents and human developers working on the \sysname{} platform, covering both the infrastructure aspects and the advanced reasoning capabilities.
