\section{Introduction}

Modern AI systems require robust infrastructure for secure hardware attestation, model verification, and resource management. \sysname{} addresses these challenges through a comprehensive microservices architecture built with Rust, emphasizing performance, security, and reliability.

\subsection{System Overview}

\sysname{} consists of five core microservices:

\begin{itemize}
    \item \textbf{API Gateway}: The entry point for external clients, handling request routing, rate limiting, and initial authentication.
    \item \textbf{Authentication Service}: Manages user accounts, authentication, and JWT token issuance.
    \item \textbf{Hardware Attestation Service}: Performs hardware checks, AI model verification, and compliance validation.
    \item \textbf{Document Service}: Handles file uploads, metadata storage, and S3 integration.
    \item \textbf{Resource Management Service}: Allocates compute resources, manages quotas, and monitors usage.
\end{itemize}

\subsection{Key Features}

The platform provides several key features essential for modern AI infrastructure:

\begin{itemize}
    \item \textbf{Security}: JWT-based authentication, bcrypt password hashing, and secure secret management.
    \item \textbf{Scalability}: Docker and Kubernetes-based deployment with horizontal scaling capabilities.
    \item \textbf{Observability}: Comprehensive monitoring through Prometheus, Grafana, and distributed tracing.
    \item \textbf{Performance}: High-performance async web services using Actix-web and Tokio.
    \item \textbf{Reliability}: Robust error handling, graceful degradation, and automated recovery mechanisms.
\end{itemize}

\subsection{Document Structure}

This document is organized as follows:

\begin{itemize}
    \item \textbf{Section 2} presents the system architecture and file structure.
    \item \textbf{Section 3} details the technology stack and implementation guidelines.
    \item \textbf{Section 4} discusses deployment, monitoring, and maintenance.
    \item \textbf{Section 5} concludes with best practices and future directions.
\end{itemize}

The documentation aims to serve as a comprehensive guide for both AI agents and human developers working on the \sysname{} platform.
